systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2004-11-09 paper/trunk/systemfit.tex
changed bibtex file to "references[.bib]"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@561 591db2bd-e0a0-4d22-8c19-2192dbb7da31
changed ugly hack with "\textcolor{white}" in \code to an empty mbox
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@562 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Summary results can be printed by\\
\code{
R>~summary(~fitsur~)~\\
~\\
systemfit~results~\\
method:~SUR~\\
\\
\textcolor{white}{.}~~N~DF~~~~~~SSR~~~~~MSE~~~~RMSE~~~~~~~R2~~~Adj~R2 \\
1~20~17~~65.6829~3.86370~1.96563~0.755019~0.726198~\\
2~20~16~104.0584~6.50365~2.55023~0.611888~0.539117~\\
~\\
The~covariance~matrix~of~the~residuals~used~for~estimation\\
\textcolor{white}{.}~~~~~~~1~~~~~~~2~\\
1~3.72539~4.13696~\\
2~4.13696~5.78444~\\
~\\
The~covariance~matrix~of~the~residuals\\
\textcolor{white}{.}~~~~~~~1~~~~~~~2~\\
1~3.86370~4.92431~\\
2~4.92431~6.50365~\\
~\\
The~correlations~of~the~residuals\\
\textcolor{white}{.}~~~~~~~~1~~~~~~~~2~\\
1~1.000000~0.982348~\\
2~0.982348~1.000000~\\
~\\
The~determinant~of~the~residual~covariance~matrix:~0.879285~\\
OLS~R-squared~value~of~the~system:~0.683453~\\
McElroy's~R-squared~value~for~the~system:~0.788722~\\
~\\
SUR~estimates~for~1~~(equation~1~)~\\
Model~Formula:~q~~~p~+~d\\
\\
\textcolor{white}{.}~~~~~~~~~~~~Estimate~Std.~Error~~~t~value~Pr(>|t|)~\\
(Intercept)~99.332894~~~7.514452~13.218913~~~~~~~~0~***~\\
p~~~~~~~~~~~-0.275486~~~0.088509~-3.112513~0.006332~~**~\\
d~~~~~~~~~~~~~0.29855~~~0.041945~~7.117605~~~~2e-06~***~\\
---~\\
Signif.~codes:~~0~`***'~0.001~`**'~0.01~`*'~0.05~`.'~0.1~`~'~1~\\
~\\
Residual~standard~error:~1.96563~on~17~degrees~of~freedom~\\
Number~of~observations:~20~Degrees~of~Freedom:~17~\\
SSR:~65.682902~MSE:~3.8637~Root~MSE:~1.96563~\\
Multiple~R-Squared:~0.755019~Adjusted~R-Squared:~0.726198~\\
~\\
~\\
SUR~estimates~for~2~~(equation~2~)~\\
Model~Formula:~q~~~p~+~f~+~a\\
\\
\textcolor{white}{.}~~~~~~~~~~~~Estimate~Std.~Error~~t~value~Pr(>|t|)~\\
(Intercept)~61.966166~~~11.08079~5.592215~~~~4e-05~***~\\
p~~~~~~~~~~~~0.146884~~~0.094435~1.555397~0.139408~\\
f~~~~~~~~~~~~0.214004~~~0.039868~5.367761~~6.3e-05~***~\\
a~~~~~~~~~~~~0.339304~~~0.067911~4.996283~0.000132~***~\\
---~\\
Signif.~codes:~~0~`***'~0.001~`**'~0.01~`*'~0.05~`.'~0.1~`~'~1~\\
~\\
Residual~standard~error:~2.550226~on~16~degrees~of~freedom~\\
Number~of~observations:~20~Degrees~of~Freedom:~16~\\
SSR:~104.05843~MSE:~6.503652~Root~MSE:~2.550226~\\
Multiple~R-Squared:~0.611888~Adjusted~R-Squared:~0.539117~\\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Equation labels}
The optional argument \code{eqnlabels} allows the user to label the equations.
It has to be a vector of strings naming the equations.\\
\code{
R>~fitsur~<-~systemfit(~"SUR",~list(~q~~~p~+~d,~q~~~p~+~f~+~a~),\\~
R+~~~~eqnlabels~=~c(~"demand",~"supply"~)~)\\
R>~summary(~fitsur~)\\
systemfit~results\\
method:~SUR\\
\\
\textcolor{white}{.}~~~~~~~N~DF~~~~~~SSR~~~~~MSE~~~~RMSE~~~~~~~R2~~~Adj~R2\\
demand~20~17~~65.6829~3.86370~1.96563~0.755019~0.726198\\
supply~20~16~104.0584~6.50365~2.55023~0.611888~0.539117\\
\ldots\\
}
If no equation labels are provided, the equations are numbered.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{/home/suapm095/Documents/Literatur/arne}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Summary results can be printed by\\
\code{
R>~summary(~fitsur~)~\\
~\\
systemfit~results~\\
method:~SUR~\\
\\
\mbox{}~~~N~DF~~~~~~SSR~~~~~MSE~~~~RMSE~~~~~~~R2~~~Adj~R2 \\
1~20~17~~65.6829~3.86370~1.96563~0.755019~0.726198~\\
2~20~16~104.0584~6.50365~2.55023~0.611888~0.539117~\\
~\\
The~covariance~matrix~of~the~residuals~used~for~estimation\\
\mbox{}~~~~~~~~1~~~~~~~2~\\
1~3.72539~4.13696~\\
2~4.13696~5.78444~\\
~\\
The~covariance~matrix~of~the~residuals\\
\mbox{}~~~~~~~~1~~~~~~~2~\\
1~3.86370~4.92431~\\
2~4.92431~6.50365~\\
~\\
The~correlations~of~the~residuals\\
\mbox{}~~~~~~~~~1~~~~~~~~2~\\
1~1.000000~0.982348~\\
2~0.982348~1.000000~\\
~\\
The~determinant~of~the~residual~covariance~matrix:~0.879285~\\
OLS~R-squared~value~of~the~system:~0.683453~\\
McElroy's~R-squared~value~for~the~system:~0.788722~\\
~\\
SUR~estimates~for~1~~(equation~1~)~\\
Model~Formula:~q~~~p~+~d\\
\\
\mbox{}~~~~~~~~~~~~~Estimate~Std.~Error~~~t~value~Pr(>|t|)~\\
(Intercept)~99.332894~~~7.514452~13.218913~~~~~~~~0~***~\\
p~~~~~~~~~~~-0.275486~~~0.088509~-3.112513~0.006332~~**~\\
d~~~~~~~~~~~~~0.29855~~~0.041945~~7.117605~~~~2e-06~***~\\
---~\\
Signif.~codes:~~0~`***'~0.001~`**'~0.01~`*'~0.05~`.'~0.1~`~'~1~\\
~\\
Residual~standard~error:~1.96563~on~17~degrees~of~freedom~\\
Number~of~observations:~20~Degrees~of~Freedom:~17~\\
SSR:~65.682902~MSE:~3.8637~Root~MSE:~1.96563~\\
Multiple~R-Squared:~0.755019~Adjusted~R-Squared:~0.726198~\\
~\\
~\\
SUR~estimates~for~2~~(equation~2~)~\\
Model~Formula:~q~~~p~+~f~+~a\\
\\
\mbox{}~~~~~~~~~~~~~Estimate~Std.~Error~~t~value~Pr(>|t|)~\\
(Intercept)~61.966166~~~11.08079~5.592215~~~~4e-05~***~\\
p~~~~~~~~~~~~0.146884~~~0.094435~1.555397~0.139408~\\
f~~~~~~~~~~~~0.214004~~~0.039868~5.367761~~6.3e-05~***~\\
a~~~~~~~~~~~~0.339304~~~0.067911~4.996283~0.000132~***~\\
---~\\
Signif.~codes:~~0~`***'~0.001~`**'~0.01~`*'~0.05~`.'~0.1~`~'~1~\\
~\\
Residual~standard~error:~2.550226~on~16~degrees~of~freedom~\\
Number~of~observations:~20~Degrees~of~Freedom:~16~\\
SSR:~104.05843~MSE:~6.503652~Root~MSE:~2.550226~\\
Multiple~R-Squared:~0.611888~Adjusted~R-Squared:~0.539117~\\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Equation labels}
The optional argument \code{eqnlabels} allows the user to label the equations.
It has to be a vector of strings naming the equations.\\
\code{
R>~fitsur~<-~systemfit(~"SUR",~list(~q~~~p~+~d,~q~~~p~+~f~+~a~),\\~
R+~~~~eqnlabels~=~c(~"demand",~"supply"~)~)\\
R>~summary(~fitsur~)\\
systemfit~results\\
method:~SUR\\
\\
\mbox{}~~~~~~~~N~DF~~~~~~SSR~~~~~MSE~~~~RMSE~~~~~~~R2~~~Adj~R2\\
demand~20~17~~65.6829~3.86370~1.96563~0.755019~0.726198\\
supply~20~16~104.0584~6.50365~2.55023~0.611888~0.539117\\
\ldots\\
}
If no equation labels are provided, the equations are numbered.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references} % a subset of my big bibtex file
%\bibliography{/home/suapm095/Documents/Literatur/arne}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
